Simulating High-Dimensional Multivariate Data

### 2021-02-24 050-examples.Rmd
begin work converting to julia

```{r ch050-LoadLib, echo = FALSE, eval = TRUE, message=FALSE, warning=FALSE, results = "hide", cache=F}
## knitr::opts_chunk$set(echo = FALSE, cache = FALSE)
# reticulate::use_condaenv("bigsimr")
library(bigsimr)
library(tidyverse)
cores <- as.integer( parallel::detectCores() - 1 )
set.seed(10142020)
```

>>>>

```{r ch050-LoadLib, echo = FALSE, eval = TRUE, message=FALSE, warning=FALSE, results = "hide", cache=F}
## knitr::opts_chunk$set(echo = FALSE, cache = FALSE)
# reticulate::use_condaenv("bigsimr")
library(bigsimr)
# bs <- bigsimr_setup(JULIA_HOME = "/usr/local/bin/")
bs <- bigsimr_setup()
dist <- distributions_setup() # Julia distributions
library(tidyverse)
cores <- as.integer( parallel::detectCores() - 1 )
set.seed(10142020)
```
